DeFi-ing Cyber Attacks

### 2022-04-26 outputs/paper/paper.Rmd
added conclusion section, final updates

Imagine a world where financial services are available to anyone, from any location, 24 hours a day, 7 days a week, without the need for any intermediaries. One where financial transactions are fully automated, eliminating the need for any intermediary financial institutions, reducing human error and lowering transactions fees. All transactions are stored on a public, open-source ledger, allowing for complete transparency. Such a world is becoming increasingly feasible by the day, and the key to achieving it lies in decentralized finance (DeFi). DeFi is a completely open source and decentralized ecosystem running on blockchain technology that offers users financial services such as loans, payments, asset management and derivatives, as well as access to decentralized crypto exchanges (DEXes). DeFi minimizes--and in many cases eliminates-- the need for centralized institutions such as banks or brokerages. Interactions on DeFi are peer-to-peer and are completed via smart contracts, self-executing computer programs functioning as contracts between parties that automatically execute when certain pre-set conditions are met. As such, DeFi aims to return control over individual's finances back to the individual, restoring freedom of choice to the financial industry. The near-unlimited potential of DeFi has not gone unnoticed, with the industry as a whole experiencing incredible growth. DeFi's current market cap is \$147 billion as of April 2022, up from $2 Billion two years ago (@coinGecko), an annual growth rate of 757.32%. One of the primary drivers of this growth is a design principle known as "permissionless composability", wherein developers are able to employ any combination of pre-existing DeFi protocols, without requiring any permissions, in order to fulfill specific use cases. This allows developers to create and interact with limitless combinations of protocols, without any third party controlling any aspect of the network activity, creating a seamless and frictionless innovation cycle wherein users can build off of each others work. Indeed, permissionless composability is one of the fundamental innovations that has allowed DeFi to grow so quickly. However, this growth has not been without setbacks. One of the primary drawbacks to DeFi is its vulnerability to hackers. By nature of the way composability allows applications to work on top of each other, if the base chain was to suffer an attack, all of the applications built on top of it would also be at risk. As well, as transactions are executed automatically via smart contracts and without human oversight, this means that a bug in a smart contract can be exploited by hackers and used to reroute funds from the transaction. Due to these risks, identifying and preventing possible attacks is one of the primary focuses of the DeFi community at the moment. Using data collected by DEFIYIELD and scraped by Octoparse as well as secondary data from DefiLlama, this paper will analyze data on the 200 costliest attacks in decentralized finance in order to identify which types of attacks are most common, most costly, and most dangerous to particular chains. This is done with the overarching goal of determining where DeFi cybersecurity efforts would best be focused on both an industry level and individual level.

@@

The final aspect of the data I will analyze is the attack data for individual chains. Of the chains in our data set, only Ethereum, BSC and Polygon have witnessed enough attacks for the data to be statistically significant and interesting. Figure \@ref(fig:attackpropbychain) shows the number of attacks on these chains, broken down by type of attack, so that we may see if certain chains are particularly vulnerable to certain types of attacks. Here we see that exit scams account for a noticeably smaller proportion of attacks on Ethereum compared to other chains, with BSC experiencing 38% more exit scam attacks in total than Ethereum, despite experiencing 39.6% less attacks in total. Exit scams accounted for 50%, 42.9% and 29.5% of the attacks on Solana, Polygon and BSC respectively, compared to only 13% of attacks on Ethereum, indicating that Ethereum is particularly secure against exit scams. On the other hand, we see that Ethereum is disproportionately affected by access control attacks, which account for 16.2% of attacks on ETH, compared to only 6.9% of attacks on BSC, and 0% of the attacks on Solana or Polygon. As well, ETH is the only chain to have experienced a honeypot exploit, which account for 5.1% of ETH attacks. Interestingly, flash loans account for a very similar proportion of attacks on ETH, BSC and Polygon, at 19.2%, , 21.3% and 28.6% respectively, while not Solana did not experience any such attacks.

@@

## Weaknesses and next steps

There are some weaknesses in

@@

  * Chain:

>>>>

Imagine a world where financial services are available to anyone, from any location, 24 hours a day, 7 days a week, without the need for any intermediaries. One where financial transactions are fully automated, eliminating the need for any intermediary financial institutions, reducing human error and lowering transaction fees. All transactions are stored on a public, open-source ledger, allowing for complete transparency. Such a world is becoming increasingly feasible by the day, and the key to achieving it lies in decentralized finance (DeFi). DeFi is a completely open source and decentralized ecosystem running on blockchain technology that offers users financial services such as loans, payments, asset management and derivatives, as well as access to decentralized crypto exchanges (DEXes). DeFi minimizes--and in many cases eliminates-- the need for centralized institutions such as banks or brokerages. Interactions on DeFi are peer-to-peer and are completed via smart contracts, self-executing computer programs functioning as contracts between parties that automatically execute when certain pre-set conditions are met. As such, DeFi aims to return control over individual's finances back to the individual, restoring freedom of choice to the financial industry. The near-unlimited potential of DeFi has not gone unnoticed, with the industry as a whole experiencing incredible growth. DeFi's current market cap is \$147 billion as of April 2022, up from $2 Billion two years ago (@coinGecko), an annual growth rate of 757.32%. One of the primary drivers of this growth is a design principle known as "permissionless composability", wherein developers are able to employ any combination of pre-existing DeFi protocols, without requiring any permissions, in order to fulfill specific use cases. This allows developers to create and interact with limitless combinations of protocols, without any third party controlling any aspect of the network activity, creating a seamless and frictionless innovation cycle wherein users can build off of each others work. Indeed, permissionless composability is one of the fundamental innovations that has allowed DeFi to grow so quickly. However, this growth has not been without setbacks. One of the primary drawbacks to DeFi is its vulnerability to hackers. By nature of the way composability allows applications to work on top of each other, if the base chain was to suffer an attack, all of the applications built on top of it would also be at risk. As well, as transactions are executed automatically via smart contracts and without human oversight, this means that a bug in a smart contract can be exploited by hackers and used to reroute funds from the transaction. Due to these risks, identifying and preventing possible attacks is one of the primary focuses of the DeFi community at the moment. Using data collected by DEFIYIELD and scraped by Octoparse as well as secondary data from DefiLlama, this paper will analyze data on the 200 costliest attacks in decentralized finance in order to identify which types of attacks are most common, most costly, and most dangerous to particular chains. This is done with the overarching goal of determining where DeFi cybersecurity efforts would best be focused on both an industry level and individual level.

@@

The final aspect of the data I will analyze is the attack data for individual chains. Of the chains in our data set, only Ethereum, BSC and Polygon have witnessed enough attacks for the data to be statistically significant and interesting. Figure \@ref(fig:attackpropbychain) shows the number of attacks on these chains, broken down by type of attack, so that we may see if certain chains are particularly vulnerable to certain types of attacks. Here we see that exit scams account for a noticeably smaller proportion of attacks on Ethereum compared to other chains, with BSC experiencing 38% more exit scam attacks in total than Ethereum, despite experiencing 39.6% less attacks in total. Exit scams accounted for 50%, 42.9% and 29.5% of the attacks on Solana, Polygon and BSC respectively, compared to only 13% of attacks on Ethereum, indicating that Ethereum is particularly secure against exit scams. On the other hand, we see that Ethereum is disproportionately affected by access control attacks, which account for 16.2% of attacks on ETH, compared to only 6.9% of attacks on BSC, and 0% of the attacks on Solana or Polygon. As well, ETH is the only chain to have experienced a honeypot exploit, which account for 5.1% of ETH attacks. Interestingly, flash loans account for a very similar proportion of attacks on ETH, BSC and Polygon, at 19.2%, 21.3% and 28.6% respectively, while not Solana did not experience any such attacks.

@@

## Weaknesses

There were a number of difficulties encountered while writing this report, specifically relating to data collection and formatting. In particular, the inability to download the REKT database made acquiring the data particularly tedious, and required the use of an external web data extraction software in Octoparse. While I successfully downloaded data from the database, due to limitations with the extraction software, I could only download as many data entries as could be displayed on a single page, 200 in this case. While this was enough data for a statistically meaningful analysis, it would have been incredibly insightful to have the roughly 2500 excluded data points. Despite this limitation, I was able to manually input a fair amount of data which was useful in providing additional context to the original data set. However, this in and of itself could be seen as a weakness, as this additional data is then subject to human error. As well, the format in which the data was downloaded made data visualization particularly cumbersome, with me often having to create entirely new data frames for each graph or set of graphs, making the data exploration especially complicated.

Another weakness of my analysis pertains to the data itself, and the lack of specificity seen in some of the variables, specifically when talking about the types of attacks seen. While there is a solid breakdown of the various types of attacks, it would have been insightful if some of the values--specifically exploit--were further broken down based on what aspect of the chain or project was exploited. As it stands, exploit acted as sort of an umbrella term for a number of possible issues, which made it harder to perform a more technical analysis of the attacks and led to some overcentralization in the attack data of our initial data set. The manual addition of data on all recorded attacks helped mitigate some of this overcentralization by providing further context to the data.

The final weakness of my report is that I did not answer all of my intended research questions, specifically what may precipitate an attack. Due to the lack of detailed technical data on each attack, there was simply not enough information for me to properly investigate this question. Still, the majority of my research questions were answered.

# Conclusions and Going Forward

There are a number of conclusions that can be drawn from this data. In particular, we see that honeypots are by far the most frequent type of attack across all analyzed chains, but comparatively result in far less damages than all other attacks, besides abandoned projects. The prevalence of honeypots indicates that more effort should be put into mitigating them. However, honeypots also present a unique opportunity, with the ability to research and analyze the behaviour of would-be attackers. Honeypots deployed for this reason are referred to as 'research honeypots', and can be used to proactively develop preventative defenses against hostile attacks. For this reason, as well as the low average cost of a honeypot attack, they are not a top priority in terms of attacks to defend against. Rather, that honor goes to exploits, which account for the vast majority of the top 200 costliest attacks, and are by far the most damaging attacks on average. However, because exploits can occur as a result of an oversight in the code associated with a project, chain or smart contract, they are also the hardest type of attack to combat. As well, because exploits are essentially the result of a coding error, the main defense against them would simply be to invest more money into software engineers and computer scientists to audit and inspect a projects code in order to proactively find errors before attackers do. For a given project, this could take the form of a designated team whos sole objective is to try and find exploits in the projects associated code. With regards to specific chains, we conclude that of chains with a meaningful amount of data, Ethereum reigns supreme in terms of security, while BSC appears to be less secure compared to other chains. In particular, Ethereum is especially secure against exit scams, and this is likely due in part to their extensive efforts in educating their userbase, which has invariably helped prevent other types of attacks as well. In this regard, BSC, Polygon and Solana all should invest further in user education. As the decentralized finance ecosystem continues to rapidly evolve and grow, so too will the attempts to exploit this sector for personal gain, and it is through consistent and concerted investment into cybersecurity and user education that we can work towards bulletproofing this blossoming technology so that it may reach its full potential.

@@

  * DeFi: Refers to decentralized finance, an ecosystem of financial services, products and applications that can be accessed
  anonymously, are decentralized and are built on and for public blockchains, such as Ethereum.

  * Blockchain / Chain: A decentralized database that stores encrypted blocks of data and chains them together to form a chronological
  ledger for the data. Blockchains are the fundamental innovation upon which the decentralized finance industry is built.
